Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
discussion North Carolina

harrisdata_clean <- harrisdata %>% drop_na()

@@

```{r}
#| echo: false
#| warning: false
#| message: false

expected_probs <- posterior_epred(bay_model, newdata = harrisdata)

# Calculate the median predicted probability for each observation
median_probs <- apply(expected_probs, 2, median)

# Add median predicted probabilities to `harrisdata`
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

# Calculate the average predicted support by state
predicted_support_table <- harrisdata %>%
  group_by(state) %>%
  summarize(average_predicted_support = round(mean(median_prob) * 100,2)) %>%
    arrange(average_predicted_support)

#predicted_support_table <- predicted_support_table[, c("state", "average_predicted_support")]

@@

Now, if we look at @fig-supportGNN Harris had a spike in early September like many other states where she was polling around 48%, but afterwards had a minor but gradual decline 
since. Although when we take a look at our model results in @

>>>>

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-supporttable
#| tbl-cap: "Averaged predicted support for Harris by state"

expected_probs <- posterior_epred(bay_model, newdata = harrisdata)
median_probs <- apply(expected_probs, 2, median)
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

predicted_support_table <- harrisdata %>%
  group_by(state) %>%
  summarize(average_predicted_support = round(mean(median_prob) * 100,2)) %>%
    arrange(average_predicted_support)

@@

Now, if we look at @fig-supportGNN Harris had a spike in early September like many other states where she was polling around 48%, but afterwards had a minor but gradual decline 
since. Although when we take a look at our model results in @fig-modelGANM we see that our prediction is that Harris's support is predicted to increase in North Carolina.

North Carolina is a significantly difficult state to predict when we consider its Republican history, predicted support for Harris, and @fig-supportstate, where both candidates are neck and neck the chance for this state to go to either candidate is very up in the air.

We believe North Carolina will vote: **Donald Trump**
